Secure Composition of Robust and Optimising Compilers

### 2023-06-17 popl/main.tex
Stutter eq

This section defines several secure compilers, each of which robustly preserves a different property of interest (see \Cref{fig:pipeline}).
The power of the framework (\Cref{sec:compprop,sec:compcomp}) is demonstrated by composing these compilers for a secure, but optimizing, compilation chain that robustly preserves \gls{ms} and \gls{cct}.
Concretely, the section starts with a base-line definition for the used languages and extends that to define languages $\src{L_{TMS}}$ and $\trg{L}$.
For programmers using $\src{L_{TMS}}$, their mental model should be that their code is temporal memory safe and cryptographic constant time.
The former is enforced by the static semantics of $\src{L_{TMS}}$, where each well-typed program is temporal memory safe.
The latter is completely untyped.
Having languages defined, this section continues with a compiler $\cc{\src{L_{\tmssafe}}}{\trg{L}}$ and proves that $\cc{\src{L_{\tmssafe}}}{\trg{L}}$ robustly preserves \gls{tms} (\Cref{subsec:cs:tms}).
For readability purposes, it defines $\irl{L_{MS}}$ to be exactly the same as $\trg{L}$ and continues to present a compiler $\cc{\trg{L}}{\irl{L_{MS}}}$ that robustly preserves \gls{sms} (\Cref{subsec:cs:ms}).
Now leaveraging the power of the framework that this paper introduces (\Cref{sec:compcomp,sec:compprop}), a compiler $\rtp{\cc{\src{L_{TMS}}}{\irl{L_{MS}}}}{\mssafe}$ is attained.
The next steps in the compilation pipeline are two secure compilers $\cc[_{\gls{dce}}]{\irl{L_{MS}}}{\irl{L_{MS}}}$ and $\cc[_{\gls{cf}}]{\irl{L_{MS}}}{\irl{L_{MS}}}$ that perform \gls{dce} and \gls{cf}, respectively, to model an optimzing pipeline happening somewhere in the compilation chain (\Cref{subsec:cs:opts}).
Finally, this section defines the language $\obj{L_{\scctsafe}}$ that is, in contrast to the other languages, not cryptographic constant time by definition.
Concluding, a compiler $\cc{\irl{L_{MS}}}{\obj{L_{CCT}}}$ that robustly preserves \gls{cct} (\Cref{subsec:cs:scct}) is shown and composed with $\cc{\src{L_{TMS}}}{\irl{L_{MS}}}$ and the optimizing compilers $\cc[_{\gls{dce}}]{\irl{L_{MS}}}{\irl{L_{MS}}}$ and $\cc[_{\gls{cf}}]{\irl{L_{MS}}}{\irl{L_{MS}}}$.
In turn, this yields $\cc{\src{L_{TMS}}}{\obj{L_{CCT}}}$, a compiler that robustly preserves a combination of \gls{ms} and \gls{cct}.

>>>>

This section defines several secure compilers, each of which robustly preserves a different property of interest (\Cref{fig:pipeline}).
The power of the framework (\Cref{sec:compprop,sec:compcomp}) is demonstrated by composing these compilers for a secure, but optimizing, compilation chain that robustly preserves \gls{ms} and \gls{cct}.
Concretely, the section starts with a base-line definition for the used languages and extends that to define languages $\src{L_{TMS}}$ and $\trg{L}$.
For programmers using $\src{L_{TMS}}$, their mental model should be that their code is temporal memory safe and cryptographic constant time.
The former is proven to be enforced by the static semantics of $\src{L_{TMS}}$, where each well-typed program is temporal memory safe.
The latter is completely untyped.
Having languages defined, this section continues with a compiler $\cc{\src{L_{\tmssafe}}}{\trg{L}}$ and proves that $\cc{\src{L_{\tmssafe}}}{\trg{L}}$ robustly preserves \gls{tms} (\Cref{subsec:cs:tms}).
For readability purposes, it defines $\irl{L_{MS}}$ to be exactly the same as $\trg{L}$ and continues to present a compiler $\cc{\trg{L}}{\irl{L_{MS}}}$ that robustly preserves \gls{sms} (\Cref{subsec:cs:ms}).
Now leaveraging the power of the framework that this paper introduces (\Cref{sec:compcomp,sec:compprop}), a compiler $\rtp{\cc{\src{L_{TMS}}}{\irl{L_{MS}}}}{\mssafe}$ is attained.
The next steps in the compilation pipeline are two secure compilers $\cc[_{\gls{dce}}]{\irl{L_{MS}}}{\irl{L_{MS}}}$ and $\cc[_{\gls{cf}}]{\irl{L_{MS}}}{\irl{L_{MS}}}$ that perform \glsfirst{dce} and \glsfirst{cf}, respectively, to model an optimzing pipeline happening somewhere in the compilation chain (\Cref{subsec:cs:opts}).
Finally, this section defines the language $\obj{L_{\scctsafe}}$ that is, in contrast to the other languages, not cryptographic constant time by definition.
Concluding, a compiler $\cc{\irl{L_{MS}}}{\obj{L_{CCT}}}$ that robustly preserves \gls{cct} (\Cref{subsec:cs:scct}) is shown and composed with $\cc{\src{L_{TMS}}}{\irl{L_{MS}}}$ and the optimizing compilers $\cc[_{\gls{dce}}]{\irl{L_{MS}}}{\irl{L_{MS}}}$ and $\cc[_{\gls{cf}}]{\irl{L_{MS}}}{\irl{L_{MS}}}$.
In turn, this yields $\cc{\src{L_{TMS}}}{\obj{L_{CCT}}}$, a compiler that robustly preserves a combination of \gls{ms} and \gls{cct}.
